Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-06 manuscript/manuscript.Rmd
updates ms fig 2 to show differences from mean cover, matches better with sensitivity analysis

```{r figure_2, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_percdiffs.rds")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

@@

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
# ggplot(climSimsQBM)+
#   geom_boxplot(aes(x=species, y=cover*100, fill=sim), outlier.size=0)+
#   theme_bw()+
#   coord_cartesian(ylim=c(0,50))+
#   scale_fill_manual(name="", labels=c("Observed", "1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)
ggplot(diff_df, aes(x=sim, y=value, fill=type))+
  geom_bar(stat="identity", position="dodge")+
  geom_hline(aes(yintercept=0))+
  scale_fill_manual(values = myCols2[c(1,3)], name="Model type")+
  xlab("Climatic change")+
  ylab("Proportional change in percent cover")+
  facet_wrap("variable", scales = "free")+
  scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

# climSimsQBMavg <- ddply(climSimsQBM, .(sim, species), summarise,
#                         avgCover = median(cover))
# climSimQBMcast <- dcast(climSimsQBMavg, formula = species~sim)
# climSimQBMcast$diffP <- with(climSimQBMcast, (Precipitation*100)-(Observed*100)) 
# climSimQBMcast$diffT <- with(climSimQBMcast, (Temperature*100)-(Observed*100))
# climSimQBMcast$diffB <- with(climSimQBMcast, (Both*100)-(Observed*100))
# climSimQBMplot <- melt(climSimQBMcast)
# climSimQBMplot <- subset(climSimQBMplot, species!="POSE")
# 
# ggplot(data=subset(climSimQBMplot, variable=="diffP"|variable=="diffT"|variable=="diffB"))+
#   geom_bar(aes(x=species, y=value, fill=variable), stat="identity", position="dodge", color="white")+
#   scale_fill_manual(name="", labels=c("1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)+
#   theme_bw()+
#   theme(legend.position=c(0.6, 0.8))+
#   ylab("Cover Change (%)")+
#   xlab("Species")
```

>>>>

```{r figure_2, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=8.5, fig.height=3, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_percdiffs.rds")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

@@

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
# ggplot(climSimsQBM)+
#   geom_boxplot(aes(x=species, y=cover*100, fill=sim), outlier.size=0)+
#   theme_bw()+
#   coord_cartesian(ylim=c(0,50))+
#   scale_fill_manual(name="", labels=c("Observed", "1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)
ggplot(diff_df, aes(x=sim, y=value, fill=type))+
  geom_bar(stat="identity", position="dodge")+
  geom_hline(aes(yintercept=0))+
  scale_fill_manual(values = myCols2[c(1,3)], name="Model type")+
  xlab("Climatic change")+
  ylab("Proportional change in percent cover")+
  facet_grid(.~variable)+
  scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()
```

.
